### 2018-08-22 Sections/protocols_for_the_quantum_internet.tex
rayleigh

>>>>

For the direct imaging of an object, diffraction limits the resolution of the image. When we consider two neighbouring points on the object separated by a small angle, the minimum angular separation resolvable is

\begin{align}
\theta_{min} = 1.22 \lambda/D
\end{align}
\noindent known as the Rayleigh criterion, $D$ being the diameter of the aperture.
% 
Current optical interferometers have limited baseline lengths, and thus limited resolution. In principle one can build a telescope array with an arbitrary D, however, phase-locking the entire system is extremely difficult over long distances.
A quantum information protocol has been developed to side-step this problem.
